---
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

### Linking graphs 

1. Linking graphs with shiny

2. Linking views without shiny

```{r}
library(tidyverse)
library(plotly)
library(crosstalk)

```

### Example 1

As shown in Linking views with shiny, the key attribute provides a way to attach a key (i.e., ID) to graphical elements – an essential feature when making graphical queries. When linking views in plotly outside of shiny, the suggested way to attach a key to graphical elements is via the SharedData class from the crosstalk package (Cheng 2016). At the very least, the new() method for this class requires a data frame, and a key variable. Lets suppose we’re interested in making comparisons of housing sales across cities for a given year using the txhousing dataset. Given that interest, we may want to make graphical queries that condition on a year, so we start by creating a SharedData object with year as the shared key.

```{r, eval=FALSE}
sd <- SharedData$new(txhousing, ~year)
p <- ggplot(sd, aes(month, median)) +
  geom_line(aes(group = year)) + 
  geom_smooth(data = txhousing, method = "gam") + 
  facet_wrap(~ city)

ggplotly(p, tooltip = "year") %>%
  highlight(defaultValues = 2015, color = "red")

```

```{r}
d <- SharedData$new(iris)
p <- GGally::ggpairs(d, aes(color = Species), columns = 1:4)
highlight(ggplotly(p), on = "plotly_selected")

```

```{r}
library(ggplot2)

df <- data.frame(f1=factor(rbinom(100, 1, 0.45), label=c("m","w")), 
                 f2=factor(rbinom(100, 1, 0.45), label=c("young","old")),
                 boxthis=rnorm(100))
df$id <- 1:100
df$f1f2 <- interaction(df$f1, df$f2)
d <- SharedData$new(df, ~id)
p1 <- ggplot(aes(y = boxthis, x = f1f2), data = d) + geom_boxplot(outlier.shape=NA) + #avoid plotting outliers twice
  geom_jitter(position=position_jitter(width=.1, height=0))

p2 <- ggplot(aes(y = boxthis, x = f1), data = d) + geom_boxplot(outlier.shape=NA) + #avoid plotting outliers twice
  geom_jitter(position=position_jitter(width=.1, height=0))

highlight(
  subplot(
  ggplotly(p1, tooltip = "id"),
  ggplotly(p2, tooltip = "id")),
 on = "plotly_hover")

```

```{r}
d <- SharedData$new(df,~id)
p1 <- ggplot(aes(y = boxthis, x = f1f2), data = d) + geom_boxplot() 

p2 <- ggplot(aes(y = boxthis, x = f1), data = d) + geom_boxplot() 

highlight(
  subplot(
  ggplotly(p1),
  ggplotly(p2)),
on = "plotly_click")


```