---
title: "Plotly"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, warning = FALSE, message = FALSE)
```

## Package

```{r}
library(tidyverse)
library(plotly)

```

## About plotly

- plotly uses the htmlwidget framework, which allows plots to work seamlessly and consistently in various contexts.

- ggplot: take a dataframe and a mapping from data variables to visual aesthetics. ggplot2 won't know how to geometrically represent the mapping until we add a layer to the plot via one of `geom_*()` or `stat_*()` functions.

- Main functions

    + `plot_ly()`: transforms data into a plotly object.
    
    + `ggplotly()`: transforms a ggplot object into a plotly object.

To ensure plotly is installed correctly.

```{r}
plot_ly(z=~volcano)

```

## Working with plotly

1. First create a plot with ggplot. 

```{r}
p <- ggplot(txhousing, aes(date, median)) +
  geom_line(aes(group = city), alpha = 0.2)
p

```

2. The `ggplotly()` function: converts a ggplot object to a plotly object.


## Arranging multiple htmlwidgets with flexbox

```{r, eval=FALSE}
library(shiny)
fluidPage(
  fluidPage(
    fluidRow(p),
    fluidRow(
      column(6, p), column(6, p)
    )
  )
)

```




